\LARGE \bf The Battle for Filter Supremacy: A Retrospective: The Movie: The Game: The Paper

### 2014-12-30 Report/project_report.tex
Redid null space trick plots

However, the EKF assumes that measurement errors are linear in the error in the state and have an additive zero-mean Gaussian noise component that is \textit{uncorrelated} to the error in the state.
Since the error in the feature positions \textit{is} correlated to the error in the state, $\Vec{r}^{(j)}$ cannot be used in the EKF directly.
Figure \ref{fig:nullspace} shows the effect of attempting to use this error directly in the EKF.
The correlation between the measurement error and the state causes the filter to behave very poorly after a small number of time steps.

@@

    \caption{Effect of nullspace projection on MSCKF performance. The correlation between the measurement error and the state causes the filter to behave very poorly after a small number of time steps.}
    \label{fig:nullspace}
\end{figure}

>>>>

However, the EKF assumes that measurement errors are linear in the error in the state and have an additive zero-mean Gaussian noise component that is \textit{uncorrelated} to the error in the state.
Since the error in the feature positions \textit{is} correlated to the error in the state, $\Vec{r}^{(j)}$ cannot be used in the EKF directly.
Figure \ref{fig:nullspace} shows the effect of attempting to use this error directly in the EKF.
The correlation between the measurement error and the state causes the filter estimates to drift further from the true values.

@@

    \caption{Effect of nullspace projection on MSCKF performance in a synthetic 100-feature dataset. The correlation between the measurement error and the state causes the filter estimates to drift further from the true values.}
    \label{fig:nullspace}
\end{figure}
